---
title: "Übung 5"
description: |
  Pupillengrösse und Cognitive Load.
date: "April 28, 2021"
author:
  - first_name: "Andrew"
    last_name: "Ellis"
    url: https://github.com/awellis
    affiliation: Kognitive Psychologie, Wahrnehmung und Methodenlehre, Universität Bern 
    affiliation_url: https://www.kog.psy.unibe.ch
    orcid_id: 0000-0002-2788-936X

citation_url: https://kogpsy.github.io/neuroscicomplab/exercise-5.html
# slug: ellis2021overview
bibliography: bibliography.bib
output: 
    distill::distill_article:
      toc: true
      toc_float: true
      toc_depth: 2
      code_folding: false
---


:::exercise

Die Aufgaben, die Sie bearbeiten sollen, finden Sie in einem gelben Kasten. Optionale Aufgaben sind in orangen Kästen.

Sie haben für diese Übung 8 Tage Zeit. Laden Sie Ihre Lösung als Rmarkdown File bis **Donnerstag, 6. Mai um 00:00 Uhr**, in den Order für Übung 5 auf ILIAS. Falls Rmarkdown nicht funkionieren sollte, werden auch Lösungen in Form eines R Skriptes akzeptiert. Nennen Sie Ihr File *Matrikelnummer_Nachname_uebung-5.Rmd* oder *Matrikelnummer_Nachname_uebung-5.R*, z. B. *15-172-874_Nachname_uebung-5.Rmd*.

Bevor Sie einreichen, vergewissern Sie sich bitte, dass Ihr Rmarkdown File geknittet werden kann, und dass der R Code ohne Fehler läuft.
:::





# Aufgabenstellung


For this example, we’ll use the data of one participant’s pupil size of the control experiment of Wahn et al. (2016) averaged by trial, df_pupil from the package bcogsci. In this experiment, a participant covertly tracked between zero and five objects among several randomly moving objects on a computer screen. This task is called multiple object tracking (or MOT: Pylyshyn and Storm 1988) task. First, several objects appear on the screen, and a subset of them are indicated as “targets” at the beginning. Then, the objects start moving randomly across the screen and become indistinguishable. After several seconds, the objects stop moving and the participant need to indicate which objects were the targets. See also Figure 4.1. Our research goal is to examine how the number of moving objects being tracked, that is how the attentional load, affects pupil size.

```{r}
df_pupil_complete <- read_csv("data/df_pupil_complete.csv")
```

```{r}
df_pupil_complete <- df_pupil %>%
   mutate(c_load = load - mean(load))
```


```{r}
df_pupil  <-  read_csv("data/df_pupil.ecsv")
df_pupil <- df_pupil %>%
   mutate(c_load = load - mean(load))
```



```{r eval=FALSE, include=FALSE}
m_pupil <- brm(p_size ~ 1 + c_load,
                 data = df_pupil,
                 family = gaussian(),
                 prior = c(
                     prior(normal(1000, 500), class = Intercept),
                     prior(normal(0, 1000), class = sigma),
                     prior(normal(0, 100), class = b, coef = c_load)),
               file = "models/06-m_pupil",
               file_refit = "on_change") 
```


```{r eval=FALSE, include=FALSE}
m_complete <- brm(p_size ~ 1 + c_load + (1 + c_load),
                 data = df_pupil,
                 family = gaussian(),
                 prior = c(
                     prior(normal(1000, 500), class = Intercept),
                     prior(normal(0, 1000), class = sigma),
                     prior(normal(0, 100), class = b, coef = c_load)),
               file = "models/06-m_complete",
               file_refit = "on_change") 
```

